FEM Model Analysis

### 2021-08-18 FEM_R/IJM_PAPER1_ALL_ANALYSES.Rmd
Committing all previous changes before cleaning up the repo and beginning work on a new feature

```{r echo=FALSE}
# Collect all conditions (and both genders) into a list, and apply the function above to that list
# cd_list <- unique(combined$Condition)
# gender_list <- unique(combined$Gender)
# 
# for(cd in cd_list) {
#   for(gen in gender_list) {
#     plot <- visAgeUKValid(combined, cd, gen)
#     print(plot)
#   }
# }
```

@@

### Split by Activity Level
```{r}
b <- b_rep
h <- h_rep

d.exstat1 <- data.frame(b$year, b$rep, b$d_age_exstat1, h$d_age_exstat1)
d.exstat1 <- d.exstat1 %>%
                dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_exstat1, 'Intervention' = h.d_age_exstat1)
d.exstat1.pivot <- pivot_longer(d.exstat1,
                              cols = Baseline:Intervention,
                              names_to = 'Source',
                              values_to = 'Life_Expectancy')
p1 <- ggplot(data = d.exstat1.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
      geom_smooth(lwd = 0.5) +
      labs(title = 'Low', x = 'Year', y = 'Life Expectancy')
p1

d.exstat2 <- data.frame(b$year, b$rep, b$d_age_exstat2, h$d_age_exstat2)
d.exstat2 <- d.exstat2 %>%
                dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_exstat2, 'Intervention' = h.d_age_exstat2)
d.exstat2.pivot <- pivot_longer(d.exstat2,
                              cols = Baseline:Intervention,
                              names_to = 'Source',
                              values_to = 'Life_Expectancy')
p2 <- ggplot(data = d.exstat2.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
      geom_smooth(lwd = 0.5) +
      labs(title = 'Moderate', x = 'Year', y = 'Life Expectancy') +
      scale_fill_grey()
p2

d.exstat3 <- data.frame(b$year, b$rep, b$d_age_exstat3, h$d_age_exstat3)
d.exstat3 <- d.exstat3 %>%
                dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_exstat3, 'Intervention' = h.d_age_exstat3)
d.exstat3.pivot <- pivot_longer(d.exstat3,
                              cols = Baseline:Intervention,
                              names_to = 'Source',
                              values_to = 'Life_Expectancy')
p3 <- ggplot(data = d.exstat3.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
      geom_smooth(lwd = 0.5) +
      labs(title = 'High', x = 'Year', y = 'Life Expectancy')
p3

path <- '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/'

ggsave(filename = 'hearte_dAge_exstat1.png',
         plot = p1,
         path = path)

ggsave(filename = 'hearte_dAge_exstat2.png',
         plot = p2,
         path = path)

ggsave(filename = 'hearte_dAge_exstat3.png',
         plot = p3,
         path = path)

@@

### SplitbyEduc
```{r}
b <- b_rep
h <- h_rep

d.educ1 <- data.frame(b$year, b$rep, b$d_age_educ1, h$d_age_educ1)
d.educ1 <- d.educ1 %>%
                dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_educ1, 'Intervention' = h.d_age_educ1)
d.educ1.pivot <- pivot_longer(d.educ1,
                              cols = Baseline:Intervention,
                              names_to = 'Source',
                              values_to = 'Life_Expectancy')
p1 <- ggplot(data = d.educ1.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
      geom_smooth(lwd = 0.5) +
      labs(title = 'Low', x = 'Year', y = 'Life Expectancy')
p1

d.educ2 <- data.frame(b$year, b$rep, b$d_age_educ2, h$d_age_educ2)
d.educ2 <- d.educ2 %>%
                dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_educ2, 'Intervention' = h.d_age_educ2)
d.educ2.pivot <- pivot_longer(d.educ2,
                              cols = Baseline:Intervention,
                              names_to = 'Source',
                              values_to = 'Life_Expectancy')
p2 <- ggplot(data = d.educ2.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
      geom_smooth(lwd = 0.5) +
      labs(title = 'Moderate', x = 'Year', y = 'Life Expectancy') +
      scale_fill_grey()
p2

d.educ3 <- data.frame(b$year, b$rep, b$d_age_educ3, h$d_age_educ3)
d.educ3 <- d.educ3 %>%
                dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_educ3, 'Intervention' = h.d_age_educ3)
d.educ3.pivot <- pivot_longer(d.educ3,
                              cols = Baseline:Intervention,
                              names_to = 'Source',
                              values_to = 'Life_Expectancy')
p3 <- ggplot(data = d.educ3.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
      geom_smooth(lwd = 0.5) +
      labs(title = 'High', x = 'Year', y = 'Life Expectancy')
p3

path <- '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/test/'

ggsave(filename = 'hearte_dAge_educ1.png',
         plot = p1,
         path = path)

ggsave(filename = 'hearte_dAge_educ2.png',
         plot = p2,
         path = path)

ggsave(filename = 'hearte_dAge_educ3.png',
         plot = p3,
         path = path)

@@

c_rep <- read_dta('output/COMPLETE/ELSA_core_cohort/ELSA_core_cohort_by_rep.dta')
s_rep <- read_dta('output/SCENARIO/ELSA_core_remove_smoken/ELSA_core_remove_smoken_by_rep.dta')

@@

>>>>

```{r echo=FALSE}
# # Collect all conditions (and both genders) into a list, and apply the function above to that list
# cd_list <- unique(combined$Condition)
# gender_list <- unique(combined$Gender)
# 
# for(cd in cd_list) {
#   for(gen in gender_list) {
#     plot <- visAgeUKValid(combined, cd, gen)
#     print(plot)
#   }
# }
```

@@

### Split by Activity Level
```{r echo=FALSE}
# b_rep <- read_dta('output/SCENARIO/ELSA_core_base/ELSA_core_base_by_rep.dta')
# h_rep <- read_dta('output/SCENARIO/ELSA_core_remove_hearte_p/ELSA_core_remove_hearte_p_by_rep.dta')
# 
# b <- b_rep
# h <- h_rep
# 
# d.exstat1 <- data.frame(b$year, b$rep, b$d_age_exstat1, h$d_age_exstat1)
# d.exstat1 <- d.exstat1 %>%
#                 dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_exstat1, 'Intervention' = h.d_age_exstat1)
# d.exstat1.pivot <- pivot_longer(d.exstat1,
#                               cols = Baseline:Intervention,
#                               names_to = 'Source',
#                               values_to = 'Life_Expectancy')
# p1 <- ggplot(data = d.exstat1.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
#       geom_smooth(lwd = 0.5) +
#       labs(title = 'Low', x = 'Year', y = 'Life Expectancy')
# p1
# 
# d.exstat2 <- data.frame(b$year, b$rep, b$d_age_exstat2, h$d_age_exstat2)
# d.exstat2 <- d.exstat2 %>%
#                 dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_exstat2, 'Intervention' = h.d_age_exstat2)
# d.exstat2.pivot <- pivot_longer(d.exstat2,
#                               cols = Baseline:Intervention,
#                               names_to = 'Source',
#                               values_to = 'Life_Expectancy')
# p2 <- ggplot(data = d.exstat2.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
#       geom_smooth(lwd = 0.5) +
#       labs(title = 'Moderate', x = 'Year', y = 'Life Expectancy') +
#       scale_fill_grey()
# p2
# 
# d.exstat3 <- data.frame(b$year, b$rep, b$d_age_exstat3, h$d_age_exstat3)
# d.exstat3 <- d.exstat3 %>%
#                 dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_exstat3, 'Intervention' = h.d_age_exstat3)
# d.exstat3.pivot <- pivot_longer(d.exstat3,
#                               cols = Baseline:Intervention,
#                               names_to = 'Source',
#                               values_to = 'Life_Expectancy')
# p3 <- ggplot(data = d.exstat3.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
#       geom_smooth(lwd = 0.5) +
#       labs(title = 'High', x = 'Year', y = 'Life Expectancy')
# p3
# 
# path <- '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/'
# 
# ggsave(filename = 'hearte_dAge_exstat1.png',
#          plot = p1,
#          path = path)
# 
# ggsave(filename = 'hearte_dAge_exstat2.png',
#          plot = p2,
#          path = path)
# 
# ggsave(filename = 'hearte_dAge_exstat3.png',
#          plot = p3,
#          path = path)

@@

### SplitbyEduc
```{r echo=FALSE}
# b <- b_rep
# h <- h_rep
# 
# d.educ1 <- data.frame(b$year, b$rep, b$d_age_educ1, h$d_age_educ1)
# d.educ1 <- d.educ1 %>%
#                 dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_educ1, 'Intervention' = h.d_age_educ1)
# d.educ1.pivot <- pivot_longer(d.educ1,
#                               cols = Baseline:Intervention,
#                               names_to = 'Source',
#                               values_to = 'Life_Expectancy')
# p1 <- ggplot(data = d.educ1.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
#       geom_smooth(lwd = 0.5) +
#       labs(title = 'Low', x = 'Year', y = 'Life Expectancy')
# p1
# 
# d.educ2 <- data.frame(b$year, b$rep, b$d_age_educ2, h$d_age_educ2)
# d.educ2 <- d.educ2 %>%
#                 dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_educ2, 'Intervention' = h.d_age_educ2)
# d.educ2.pivot <- pivot_longer(d.educ2,
#                               cols = Baseline:Intervention,
#                               names_to = 'Source',
#                               values_to = 'Life_Expectancy')
# p2 <- ggplot(data = d.educ2.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
#       geom_smooth(lwd = 0.5) +
#       labs(title = 'Moderate', x = 'Year', y = 'Life Expectancy') +
#       scale_fill_grey()
# p2
# 
# d.educ3 <- data.frame(b$year, b$rep, b$d_age_educ3, h$d_age_educ3)
# d.educ3 <- d.educ3 %>%
#                 dplyr::rename('Year' = b.year, 'Rep' = b.rep, 'Baseline' = b.d_age_educ3, 'Intervention' = h.d_age_educ3)
# d.educ3.pivot <- pivot_longer(d.educ3,
#                               cols = Baseline:Intervention,
#                               names_to = 'Source',
#                               values_to = 'Life_Expectancy')
# p3 <- ggplot(data = d.educ3.pivot, aes(x = Year, y = Life_Expectancy, color = Source)) +
#       geom_smooth(lwd = 0.5) +
#       labs(title = 'High', x = 'Year', y = 'Life Expectancy')
# p3
# 
# path <- '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/results/test/'
# 
# ggsave(filename = 'hearte_dAge_educ1.png',
#          plot = p1,
#          path = path)
# 
# ggsave(filename = 'hearte_dAge_educ2.png',
#          plot = p2,
#          path = path)
# 
# ggsave(filename = 'hearte_dAge_educ3.png',
#          plot = p3,
#          path = path)

@@

c_rep <- read_dta('output/SCENARIO/ELSA_core_cohort/ELSA_core_cohort_by_rep.dta')
s_rep <- read_dta('output/SCENARIO/ELSA_core_remove_smoken/ELSA_core_remove_smoken_by_rep.dta')

@@

# Comparing Output Values
```{r}
b <- read_dta('/home/luke/Documents/E_FEM_clean/E_FEM/output/SCENARIO/ELSA_core_base/ELSA_core_base_summary.dta')
h <- read_dta('/home/luke/Documents/E_FEM_clean/E_FEM/output/SCENARIO/ELSA_core_remove_hearte_p/ELSA_core_remove_hearte_p_summary.dta')

new.df <- data.frame(b$year, b$d_age_all, h$d_age_all)

new.df$diff <- new.df$h.d_age_all - new.df$b.d_age_all

new.df
```

### 2021-08-18 FEM_R/model_analysis_core.Rmd
Committing all previous changes before cleaning up the repo and beginning work on a new feature

```{r echo = FALSE}

#AgeUK
male_au <- read.csv('../../../Validation/AgeUK-chronDisease-MALE.csv')
female_au <- read.csv('../../../Validation/AgeUK-chronDisease-FEMALE.csv')

@@

```{r}
# Collect all conditions (and both genders) into a list, and apply the function above to that list
cd_list <- unique(combined$Condition)
gender_list <- unique(combined$Gender)

>>>>

```{r echo = FALSE}
#AgeUK
male_au <- read.csv('../../../Validation/AgeUK-chronDisease-MALE.csv')
female_au <- read.csv('../../../Validation/AgeUK-chronDisease-FEMALE.csv')

@@

```{r echo=FALSE}
# Collect all conditions (and both genders) into a list, and apply the function above to that list
cd_list <- unique(combined$Condition)
gender_list <- unique(combined$Gender)
